\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-14 paper.tex
conclusion, abstract updates

\subsection*{Abstract}
In this paper, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG. Across all participants, we achieve mean 0\% false acceptance and 0.12\% false rejection rates with data from only one earpiece with three electrodes. In a preliminary test of an "imposter'' spoofing attack, we find a 0\% false acceptance rate. Our results indicate that in-ear EEG could provide a discreet, convenient, multi-factor authentication. (TO ADD: neural source of signal confirmation, usability summary)

@@

\section{{\bfseries\sffamily TODO} Conclusion}

>>>>

\subsection*{Abstract}
In this paper, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG. Across all participants, we achieve mean 0\% false acceptance and 0.12\% false rejection rates with data from only one earpiece with three electrodes. In a preliminary test of an "imposter'' spoofing attack, we find a 0\% false acceptance rate. Our results indicate that in-ear EEG could provide a discreet, convenient, and usable protocol for multi-factor authentication in a single step, in which a user thinks their chosen passthought.

@@

\section{Conclusion}

We believe custom-fit, in-ear EEG earbuds could provide three factors of authentication in a authentication single step: thinking one's password. In this paper, we demonstrate quite high authentication accuracy using a single sensing earbud. By expanding our corpus of EEG readings (in population size, time, and diversity of settings), we hope to better understand the underlying distribution of EEG signals, so that we may better understand the security properties of passthoughts.
